%        File: letter.tex
%     Created: Fri Mar 27 12:00 PM 2015 P
% Last Change: Fri Mar 27 12:00 PM 2015 P
%
\documentclass[a4paper]{letter}
\usepackage{ulem}
\signature{Lee Mracek}
\address{10129 Lockwood Dr. \\ Cupertino, CA\quad95014}
\begin{document}
\begin{letter}{Mary Hill \\ De Anza Middle College \\ 21250 Stevens Creek Blvd \\ Cupertino, CA\quad95014}
    \opening{Dear Mary,}
    I hope that this letter does not find you too exhausted from the trials and tribulations of Middle College interviews. If you are exhausted, as expected, I hope that the candidates were at least entertaining, and that the interviews were constructive in determining your next batch of \sout{victims} students. Regardless, I think it is fairly safe to say that my week turned out to be rather unexpectedly productive. Of course, knowing the nature of finals, I should have expected it, but I guess it worked out decently either way. As of this moment, I only know one of my final grades: Computer Science, in which I got a 121 out of 125. The results for Physics, Physics Lab, and Math are not out yet, although I believe I performed adequately. I felt especially overprepared for Math 1B, and feel as though I did well enough on the final to thoroughly deserve an A in the class. In Physics, I did not need to score as highly, but I did anyway (hopefully).
    

    Quite honestly, I cannot wait until next quarter. I have not been climbing since the start of this quarter, and taking $^2/_3$ as many units as this quarter, including orchestra, which should be a breeze. I am most worried about Math 1C. The same professor I had this quarter, Millia Ison, will be teaching me next quarter, and I am now quite familiar with her class and teaching style. For CIS22B, my professor happens to be the uncle of someone I know through robotics, which obviously does not help me with the class, but it is rather interesting. Additionally, while the class is harder than 22A, I believe that with the aid of Max, Austin, and Julia, I will be completely fine.

    \closing{Sincerely,}
\end{letter}
\end{document}


