%        File: collegenow.tex
%     Created: Wed Mar 04 07:00 PM 2015 P
% Last Change: Wed Mar 04 07:00 PM 2015 P

\documentclass[a4paper]{article}
\usepackage{ifpdf}
\usepackage{mla}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\begin{document}
\begin{mla}{Lee}{Mracek}{Emmert}{College Now}{\today}{<TITLE>}
    I hate high school. Meaningless work, rigid schedules, early mornings, and constant social drama made up my first two years of ``the best four years of your life.'' Junior year, I transferred to Middle College at De Anza which certainly changed my life for the better. Without the needless classes that high school required me to take, I could build my schedule around my own interests, passions, and desire for waking up after the sun. My happiest moment in recent months occurred while walking to Coffee Society at dusk after my last De Anza class; the feeling of independence and solitude ignited a warm glow inside my chest which never manifested itself at any point in high school. Furthermore, my De Anza challenge me on a level that I did not experience in my high school classes, which greatly enriches the learning process. At Middle College, I am not able to take all the classes I want to, because of the time commitment to a two or three hour class in the middle of the day, which coincidentally coincides with the majority of the science labs that I wish to take. College Now offers the only complete educational package in FUHSD with regards to my interest through challenging De Anza classes, the promise of independence, and the freedom to chose my own schedule. \\
    I have a strong commitment to learning, and always prefer the route which allows me to learn the most. I take hard classes not to have them shine prettily on my college applications, but instead so that I may unlock yet another facet of, at least as I visualize it, the web of knowledge. I enjoy the rush that comes after understanding some new aspect of reality in any subject. The high school curriculum and style, or even the Middle College option can not provide the level of depth and breadth that makes up my ideal educational experience. Through College Now, I would be able to enroll in significantly more De Anza classes than I can in Middle College, and be able to replace the California-mandated government class with something that interests me on a higher level, such as international relations, or political science. \\
    When I am allowed or encouraged to act autonomously, and able to enjoy the solitude and freedom that comes with it, I live a much more redeeming life and am encouraged to continue to attempt to develop myself as a person and individual in my community. As a College Now student, I would be able to become truly a part of the De Anza community, and participate in the myriad events which occur at De Anza between the hours of twelve and three o'clock, such the Table Tennis Club, which meets while I am in Middle College. \\
    While my time in high school has been enormously improved by my time spent in the Middle College program, its limitations prevent me from exploring the full potential of De Anza Community College and deny me from fully fulfilling my thirst for independence and education. College Now, because of my unique desires, remains the only program that will allow me to completely explore my academic and social potential before I am dumped into the real world.
\end{mla}
\end{document}
