\documentclass[letterpaper,11pt]{article}

\usepackage{ifpdf}
\usepackage{mla}

\begin{document}
\begin{mla}{Lee}{Mracek}{Mary Hill}{American Studies}{\today}{Converted Thesis Questions}
    \begin{enumerate}
        \item Through the brief vignettes in O'Brian's novel, \textit{The Things They Carried,} it is obvious through each soldier that people should seek advice from others or else be overwhelmed by the problems that face them.

        \item Tim O'Brian's \textit{The Things They Carried,} as a microcosm of a generation, shows that in today's society and violence creativity is needed more than ever.

        \item Through O'Brian's work, \textit{The Things They Carried,} it becomes evident that the only accurate way to capture emotional stories is by telling what O'Brian calls ``true war stories.''

        \item The final fates of the soldiers in Tim O'Brian's, \textit{The Things They Carried}, show that a person cannot be responsible for the actions of others based on his own actions.
        \item Through the soldier's view of Vietnam, and the experience of Mary Anne in Vietnam, it is clear that one's perceptions of beauty may inevitably betray oneself. 

        \item Tim O'Brian's novel, \textit{The Things They Carried}, is not only an emotional war novel, but also a critique of American foreign policy during the Vietnam Era, claiming that conflict is unnecessary.

        \item O'Brian's vivid descriptions of the killing technology available in Vietnam in his book \textit{The Things They Carried}, show the reader that the benefits of technology and innovation always come to the detriment of some people's lives.

        \item In order to provide an accurate emotional retelling of his time in Vietnam, Tim O'Brian uses his novel, \textit{The Things They Carried} to expose his own inner feelings during the war by creating separate characters from them.

        \item Because of the necessity of emotional truth in stories, O'Brain in \textit{The Things They Carried} attempts to prove that stories need not be true if they convey their emotional impact.
    \end{enumerate}

    \textbf{Note: I'm not really sure which question each one came from.}
\end{mla}
\end{document}
